---
title: "Data Download"
author: "maxi kellerbauer"
date: "Thu Jan  3 20:18:42 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Download}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r eval=FALSE}
require(RSQLite)
require(stAirPol)
require(data.table)
```

Here we specify the folder where all data should be saved
Also, the time range is specified here

```{r eval=FALSE}
path = '~/data'
start_date = "2017-12-01"
end_date = "2017-12-31"


# (1) Download data: luftdaten.info ---------------------------------------
```

Download the raw csv files
Downloaded files are stored in the subfolder ./luftdaten/
NOTE: That may take some time

```{r eval=FALSE}
dir.create(path)
dir.create(paste0(path, "/luftdaten/"))
LD_download(folder = paste0(path, "/luftdaten/"), start = start_date,
            end = end_date)
```

Transform the csv files to a useful format, and store them in a
SQLite database

```{r eval=FALSE}
dir.create(paste0(path, "/db/"))
LD_sql2(start = start_date, end = end_date,
        source = paste0(path, "/luftdaten/"),
        dbname = paste0(path, "/db/"))
dir.create(paste0(path, "/db/data"))
split_db_in_months(paste0(path, "/db"))
download_sensor_age(path = path)

# (2) Download data: DWD --------------------------------------------------
```

Download wind and precipitation from the DWD
All Information’s are stored in the subfolder ./dwd

```{r eval=FALSE}
dir.create(paste0(path, "/dwd/"))
download_dwd_data(obs = 'wind', path = paste0(path, "/dwd/"))
download_dwd_data(obs = 'precipitation', path = paste0(path, "/dwd/"))
setup_station_table(paste0(path, "/dwd/"))


# (3) Download data: Open Transport Map -----------------------------------
dir.create(paste0(path, "/otm/"))
download_OTM(path = paste0(path, "/otm/"))
```

Now you are able to run 2_data_preparation.R, please use there the correct
path and a time range which is included in the time range specified here
