---
title: "Data preparation"
author: "Maxi Kellerbauer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data preparation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r }
require(data.table)
require(stAirPol)
require(ggplot2)
```

Note: for that preselected specifications are 8 datasets included in the
R-Package stAirPol
     ______________________________________________________________________
     - 'muc_airPol_p1':
       A dataset of daily observations in Munich for December 2017 of PM10
     - 'muc_airPol_p1_grid':
       A grid for 'muc_airPol_p1'
     - 'muc_airPol_p2':
     ______________________________________________________________________
     - 'muc_airPol_p2':
       A dataset of daily observations in Munich for December 2017 of PM2.5
     - 'muc_airPol_p2_grid':
       A grid for 'muc_airPol_p2'
     ______________________________________________________________________
     - 'muc_airPol_p1_8h':
       A dataset of 8h observations in Munich for December 2017 of PM10
     ______________________________________________________________________
     - 'muc_airPol_p2_8h':
       A dataset of 8h observations in Munich for December 2017 of PM2.5
     ______________________________________________________________________


If that's enough for testing, please continue with:
3_simple_modelling_and_crossvalidation.R


Specify the data path which contains the collected data.

```{r eval=FALSE}
path = '~/data'
```

For which German Postcode do you want to model air pollution data?
Use directly one Postcode or see ?get_postcodes_for_landkreis and
?get_postcodes_for_bundesland
We will take Munich for that example

```{r eval=FALSE}
m.plz <- c(80539)
```

Now you have to decide what the gridcellsize should be used, see
?sf::st_make_grid for information’s about the cellsize parameter

```{r eval=FALSE}
m.grid_cellsize <- 0.005
```

The next specification which is needed is the time range, please specify
the start and the end date
NOTE: currently are only whole months supported, so the start date is floored
and the end date is ceilinged.

```{r eval=FALSE}
start_date = "2017-12-01"
end_date = "2017-12-31"
```

The specification which is needed is the aggregation interval and the
time shift which is apply to the data. We choose an aggregation interval of 8
hours, for more information about the aggregration_interval units see
?lubridate::round_date. The time shift is applied to the data.
Run the print method on the object for more information.

```{r eval=FALSE}
m.agg_info <- aggregation_information(timeshift = lubridate::hours(0),
                                      aggregation_interval = '24 hours')
print(m.agg_info)



# Data gathering ----------------------------------------------------------
m.date_pattern <- unique(substring(as.character(seq(as.Date(start_date),
                                             as.Date(end_date), 1)), 1,7))
```

Collection the Information’s about the sensors and the collected data from
the sensors in the chosen area.

```{r eval=FALSE}
# Traffic data ------------------------------------------------------------
sensors <- get_sensors(date_pattern = m.date_pattern, plz = m.plz, path = path)
sensor_age <- get_sensor_age(path = path)
sensor_data <- get_sensor_measured_values(sensors, m.date_pattern, path = path)

```

Please note, if you want to gather data for a big area, I suggest to use a
fixed value for lambda, e.g. lambda = 0.1, because the optimization of
optim_lambda() will take a huge amount of computation costs.
lambda.p1 <- lambda.p2 <- 0.1
If an optimization is applied, please check the validation plot.
The local maximum should not be on the boarders, if it is please
specify the lambda_range parameter.

```{r eval=FALSE}
estimate_grid_size(m.plz)
roads <- get_opentransportmap_data(m.plz, path = path, trafficvol_treshold = 1)
lambda.p1 <- optim_lambda(sensor_data[['P1']], sensors[['P1']], roads = roads,
                          validation_plot = TRUE)
lambda.p2 <- optim_lambda(sensor_data[['P2']], sensors[['P2']], roads = roads,
                          validation_plot = TRUE)
grid.traffic.p1 <- make_grid_traffic(lambda.p1, m.plz)
grid.traffic.p2 <- make_grid_traffic(lambda.p2, m.plz)
data.traffic.p1 <- make_data_traffic(sensors = sensors[['P1']], lambda = lambda.p1)
data.traffic.p2 <- make_data_traffic(sensors = sensors[['P2']], lambda = lambda.p2)

# Space Time data ---------------------------------------------------------
calculate_space_time_datasets()

# Time Variables ----------------------------------------------------------
calculate_time_datasets()

# Rename datasets ---------------------------------------------------------
rename_datasets()

# Combine all calculated datasets -----------------------------------------
combine_datasets()


# Save RDS files ----------------------------------------------------------
saveRDS(data.final.p1, file = paste0(path, '/p1_model_data_',m.grid_cellsize, '.rds'))
saveRDS(grid.final.p1, file = paste0(path, '/p1_grid_data_',m.grid_cellsize, '.rds'))
saveRDS(data.final.p2, file = paste0(path, '/p2_model_data_',m.grid_cellsize, '.rds'))
saveRDS(grid.final.p2, file = paste0(path, '/p2_grid_data_',m.grid_cellsize, '.rds'))
```


