---
title: "Simple modelling and crossvalidation"
author: "Maxi Kellerbauer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simple modelling and crossvalidation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 8,
  fig.height = 6,
  comment = "#>"
)
```


# Read the data
```{r messages=FALSE,warning=FALSE, echo=FALSE, results='hide'}
require(stAirPol)
require(spTimer)
require(ggplot2)
require(data.table)
```
We load the daily data of Munich for PM2.5

```{r }
data("muc_airPol_p2")
```

remove outliers in the data

```{r }
data <- clean_model_data(muc_airPol_p2, timesIQR = 1.5)

```

# Fit the model
Now we want to fit a Gaussian Process model, and analyze the parameters and
the model himself.
We use the following formula to specify the covariables in the linear part
of the model

```{r }
formula = value ~ humi + temp + rainhist + windhist +
  trafficvol + log(sensor_age)
```

There are tree most used model types,
    - Gaussian Process short GP
    - Autoregressive Gaussian Process short AR
    - Gaussian Predictive Process short GPP
First we fit only the Gaussian Process
For more model types, see ?spT.Gibbs

```{r }
model.gp.p2 <- fit_sp_model(data = data, formula = formula, model = 'GP')
```

With summary we get a brief overview of the fitted parameters, and the PMCC
of the model

```{r }
summary(model.gp.p2)
```

Trace plots of the MCMC-Iterations
Note: make the plot window in RStudio as big as possible

```{r }
# plot(model.gp.p2)
# dev.off()
```

Now we can do a deeper specification of the Model
First, we add our own Prioris to the model, for more details see ?spT.priors

```{r }
priors <- spT.priors(model = "GP", inv.var.prior = Gamm(a = 2, b = 1),
                     beta.prior = Norm(0, 10^4))
```

Covariance function for the spatial effects we want to use the exponential
covariance, for more choices see ?spT.Gibbs

```{r }
cov.fnc = "exponential"
```

We change the method how the parameter for the spatial decay should be fitted,
see ?spT.decay for more details
We choose a Gamma(2,1) Prior distribution with the tuning parameter 0.1,
the tuning parameter should be chosen that the acceptance rate for phi is
between 20%-40%.

```{r }
spatial.decay = spT.decay(distribution = Gamm(a = 2, b = 1), tuning = 0.25)
```

If it's wanted to get some feedback during the fitting process, we can
choose a number of feedback messages we want to arrive

```{r }
report = 5
```

We are able to perform a on the fly transformations of the target variable

```{r }
scale.transform = "SQRT"
model.gp.p2.mod <- fit_sp_model(data = data,
                            formula = formula,
                            model = 'GP',
                            priors = priors,
                            cov.fnc = cov.fnc,
                            report = report,
                            scale.transform = scale.transform,
                            spatial.decay = spatial.decay)
summary(model.gp.p2.mod)
```

# Test the model
Now we have created two different kinds of Gaussian Process Models. With a
crossvalidatioin we want to the them against each other.
Therefore, we specify a train and a test set with 75% random training sensors

```{r }
training_set <- get_test_and_training_set(data, sampel_size = 0.75,
                                      random.seed = 220292)
```

Now we are able the train the models only the the chosen training sensors
by adding training_set = training_set into the function

```{r }
model.gp.p2 <- fit_sp_model(data = data, formula = formula, model = 'GP',
                            training_set = training_set)
model.gp.p2.mod <- fit_sp_model(data = data,
                                formula = formula,
                                model = 'GP',
                                priors = priors,
                                cov.fnc = cov.fnc,
                                report = report,
                                training_set = training_set,
                                scale.transform = scale.transform,
                                spatial.decay = spatial.decay)
```

we are able to perform with the well-known predict function predictions for
that models, by adding the training_set, only predictions for the test
sensors will be calculated.

```{r }
pred.gp.p2 <- predict(model.gp.p2, data, training_set)
pred.gp.p2.mod <- predict(model.gp.p2.mod, data, training_set)
```

To evaluate the predictive performance ,we use evaluate_prediction()

```{r }
evaluate_prediction(pred.gp.p2)
evaluate_prediction(pred.gp.p2.mod)
```

There are also some validation plots availible
Fitted vs. predicted:

```{r }
plot(pred.gp.p2.mod)
```

Fitted vs. predicted separated by time:

```{r }
plot(pred.gp.p2.mod, time_dimension = TRUE)
```

# Various Bayesian Models
There are more Models besides the Gaussian Process.
For example, the autoregressive Gaussian Process:

```{r }
priors.ar <- spT.priors(model = "AR",
                        inv.var.prior = Gamm(a = 2, b = 1),
                        beta.prior = Norm(0, 10^4),
                        rho.prior=Norm(0,10^10))
model.ar.p2 <- fit_sp_model(data = data,
                            formula = formula,
                            model = 'AR',
                            priors = priors.ar,
                            cov.fnc = cov.fnc,
                            report = report,
                            training_set = training_set,
                            scale.transform = scale.transform,
                            spatial.decay = spatial.decay)

pred.ar.p2 <- predict(model.ar.p2, data, training_set)
evaluate_prediction(pred.ar.p2)
```

The last model is the Gaussian Predictive Process, here we have to specify
two more things:
   - How much knots should be used?
   - How should the knots be placed?
Detailed options for that question are shown in 4_advanced_modelling.R

```{r }
priors.gpp <- spT.priors(model = "GPP", inv.var.prior = Gamm(a = 2, b = 1),
                        beta.prior = Norm(0, 10^4))
model.gpp.p2 <- fit_sp_model(data = data,
                            formula = formula,
                            model = 'GPP',
                            priors = priors.gpp,
                            cov.fnc = cov.fnc,
                            knots_count = 4,
                            report = report,
                            training_set = training_set,
                            scale.transform = scale.transform,
                            spatial.decay = spatial.decay)

pred.gpp.p2 <- predict(model.gpp.p2, data, training_set)
evaluate_prediction(pred.gpp.p2)
```

# Compair the models

```{r }
evaluate_prediction_table(list('pred.gp.p2' = pred.gp.p2,
                               'pred.gp.p2.mod' = pred.gp.p2.mod,
                               'pred.ar.p2' = pred.ar.p2,
                               'pred.gpp.p2' = pred.gpp.p2))

gridExtra::grid.arrange(grobs = list(
  plot(pred.gp.p2) + ggtitle('GP'),
  plot(pred.gp.p2.mod) + ggtitle('mod GP'),
  plot(pred.ar.p2) + ggtitle('AR'),
  plot(pred.gpp.p2) + ggtitle('GPP')
))
```
